soling

### 2021-02-01 inst/soling.Rmd
H1 - H2 now gives the difference in likelihood functions

```{r showdiff,fig.cap="Evaluate before and after incorporation round robin and quarter final information"}
H <- soling  # before new information
soling_maxp <- maxp(H) 
H %<>% rr(soling_rr1)
H %<>% rr(soling_rr2)
H %<>% rr(soling_qf)
soling_after <- H # after new information
soling_after_maxp <- maxp(soling_after)
par(pty="s")
plot(soling_maxp,soling_after_maxp,,asp=1,pch=16,xlim=c(0,0.3),ylim=c(0,0.3))
abline(0,1)
```

@@

```{r}
(soling_diff <- soling_after + (-1)*soling)
```

So `H2` is the _difference_ between `H`--- which is `soling` plus the
observations from the roundrobins and quarter finals---and `soling`
withouth the extra information.  In other words, `H2` is the simply
the information in the roundrobins and quarter finals.

>>>>

```{r showdiff,fig.cap="Evaluate before and after incorporation round robin and quarter final information"}
H <- soling  # before new information
soling_maxp <- maxp(H) 
H %<>% rr(soling_rr1)
H %<>% rr(soling_rr2)
H %<>% rr(soling_qf)
soling_after <- H # after new information
soling_after_maxp <- maxp(soling_after)
par(pty="s")
plot(soling_maxp,soling_after_maxp,asp=1,pch=16,xlim=c(0,0.3),ylim=c(0,0.3))
abline(0,1)
```

@@

```{r}
(soling_diff <- soling_after - soling)
```

So `soling_diff` is the _difference_ between `H`--- which is `soling`
plus the observations from the roundrobins and quarter finals---and
`soling` without the extra information.  In other words, the
information in the roundrobins and quarter finals.
